This doctoral degree was a transformative and intense experience, and it would not have been possible to accomplish by myself.
Without a doubt, the biggest influence on my intellectual growth has been my advisor, Joseph Casillas. 
His seminar in statistics for linguists was a life-changing course for me.
During the course, he asked us a challenging question: "What do we know, and how do we know it?". 
I took this idea and tried to run with it.
I found out that this was complex and layered question, and each time I stumbled over the many complicated steps to unpacking what counts as evidence in our work, I came back to Joseph. 
Everytime I talked to Joseph, I learned something new, whether it was about statistics, R, linguistics, or life.
I firmly believe that the cumulative value of all of these small moments was the driving force in my development, and it was a completely indispensable part of the program.
Thank you, Joseph, for everything - I would not be here without you!

I also want to thank my committee. Thank you Tom, for always being candid and wise. Thank you Jennifer, for your encouragment and perspesctive. Finally, and especially, thank you Magdalena for hosting me in Poland during my third year and for opportunity to present part of this work in Poznan. 

Thank you, also, to my friends and colleagues: Patrick Thane, Nicole Rodriguez, Gabriela Constantin-Dureci and Juan Jose Garrido. We all shared many afternoons and evenings de-stressing, talking about our work, and surviving graduate school. I will miss and cherish those times!

Last, but certainly not least, I am indebted to my family.
thank you to my wife, Marinna for your constant support, love, and care.
Your belief in me helped me through the hardest times and let me enjoy the easiest ones.
I truly don't believe I would be here without you.
Also, thank you to my daughter, Virginia, for (kind of) sleeping through the night during some of the intense stages of this work.
I will forever remember the days in which we rolled through the streets on New Brunswick together as I worked on the final portions of this dissertation. 

Thank you! 
