---
title: "Report VCT/PCT task results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(bayesplot)
source(here::here("scripts", "spanish_bilingual_pct", "00_libs.R"))
source(here::here("scripts", "spanish_bilingual_pct", "03_load_data.R"))


all_pct = read.csv(here("scripts", "spanish_bilingual_pct", 
                 "data", "tidy", "all_pct.tidy_sp.csv"))

mod = read_rds(here("scripts", "spanish_bilingual_pct", "models",
                 "bayesian_log_sp.RDS"))


df_bayesian = data.frame(fixef(mod))


report_df = read.csv(here("scripts", "spanish_bilingual_pct", 
               "data", "tidy",
               "report_bilabial_span_l1.csv"))
```

# Statistical Analysis

This is a document that converts the results of the PCT (so far) to prose. 

A Bayesian logistic regression was run `language ~ stim_language*phoneme*frame + (1 | participant), data = all_pct)`, where the outcome was language (either English or Spanish, coded as 1 and 0). The preditors were `stim_language` (either French or German), `phoneme` (i, o, schwa or y) and `frame` (fricative or bilabial). 

The priors were the default (weakly informative priors), and the model was run using brms using all other defaults. 


# Results 

A forest plot of the model can be seen below and is reported prior to further interpretation (the conversion of the log odds parameter estimates to probability).
Overall, there was a preference for English categories in this group.
The probability of choosing an English word when the French stimulus contained /i/ was `est`, probability of choosing an English category when the stimulus contained /i/ in German were `est` 

```{r}

mod_posterior <- as.matrix(mod)
plot_title <- ggtitle("Plot Title")

mcmc_areas(mod_posterior,
           pars = c("b_Intercept", 
                    "b_stim_languageGerman", 
                    "b_phonemeo",
                    "b_phonemeschwa",
                    "b_phonemey",
                    "b_framefricative",
                    "b_stim_languageGerman:phonemeo",
                    "b_stim_languageGerman:phonemeschwa",
                    "b_stim_languageGerman:phonemey",
                    "b_stim_languageGerman:framefricative",
                    "b_phonemeo:framefricative",
                    "b_phonemeschwa:framefricative",
                    "b_phonemey:framefricative",
                    "b_stim_languageGerman:phonemeo:framefricative",
                    "b_stim_languageGerman:phonemeschwa:framefricative",
                    "b_stim_languageGerman:phonemey:framefricative"),
           prob = 0.8) + plot_title

```

```{r}
report_df = read.csv(here("scripts", "spanish_bilingual_pct", 
               "data", "tidy",
               "report_bilabial_span_l1.csv"))
```


Number of participants
```{r}
length(unique(all_pct$participant))
```

List of each participant with number of trials each
```{r}
all_pct %>% 
  group_by(participant) %>% 
  summarize(n = n()) %>% 
  filter(n > 79) %>% 
  knitr::kable()
```


Number of responses per language across all stimuli
```{r}
graph_df = all_pct %>% 
  group_by(phoneme, word, stim_language, language) %>% 
  summarise("response" = n(), rating_mean = mean(rating),
            rating_sd = sd(rating)) %>% 
  filter(response > 11)

graph_df %>% 
  ggplot(aes(x = language, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("Overall Responses") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79")) 
```


```{r}
report_df %>% 
  ggplot(aes(x = estimate, y = phoneme, color = language,
             xmin=hdi_hi, xmax=hdi_lo)) + 
  geom_pointrange(position = position_dodge(width = .5), 
                  shape = 21, fill = "white") + 
  geom_vline(xintercept = .5, linetype = "dashed") +
  scale_color_manual(values=c("#1F9646", "darkgoldenrod3"))  + 
  xlab("Probability") + ylab("Phoneme of stimulus") +
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"),
        legend.position = "bottom") + 
  theme(legend.position = "bottom") + 
  ggtitle("Probability of choosing an English word")
```

# check how many phonemes total were presented
```{r}
all_pct %>% 
  group_by(phoneme) %>% 
  summarize(n = n())
```

```{r}
graph_df %>% 
  filter(phoneme == "i") %>% 
  ggplot(aes(x = word, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to /i/") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```

```{r}
graph_df %>% 
  filter(phoneme == "o") %>% 
  ggplot(aes(x = word, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to /o/") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```

```{r}
graph_df %>% 
  filter(phoneme == "o") %>% 
  ggplot(aes(x = language, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to o") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```

```{r}
graph_df %>% 
  filter(phoneme == "schwa") %>% 
  ggplot(aes(x = word, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to schwa") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```  

```{r}
graph_df %>% 
  filter(phoneme == "schwa") %>% 
  ggplot(aes(x = language, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to schwa") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```

```{r}
graph_df %>% 
  filter(phoneme == "y") %>% 
  ggplot(aes(x = word, y = response, fill = language)) + 
  geom_bar(stat = "identity") +
  ggtitle("responses to y") + facet_grid(~stim_language) +
  scale_fill_manual(values=c("#1F9646", "darkgoldenrod3")) + 
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"))
```



